NGO analysis

### 2022-07-26 Dashboard/report.Rmd
Moving CEO legend to bottom.

```{r compensation_plot, out.width="100%", fig.cap="Based on the category \`Lederlønn' in the Proff.no data. Not in thousands. Includes the entries \`Lønn' and \`Leder annen godtgjørelse'. A common measure of transparency, but should normally be evaluated in context."}
## CEO compensation-----------------------------------------------------------
CEO_plot <-
  # Testing for the presence of data
  if (sum(!is.na(htmldata$lederlonn)) == 0 &&
    sum(!is.na(htmldata$leder_annen_godtgjorelse)) == 0) {
    # Returning NA if no data
    NA
  } else {
    # Creating plot if any data exist
    # Note that the plot will still look empty, but have a legend and scales,
    # if all values are explicit zeroes
    htmldata |>
      # preparing for pivoting
      select(
        year, lederlonn, leder_annen_godtgjorelse
      ) |>
      # Compensation in ordinary numbers
      mutate(
        lederlonn = lederlonn * 1000,
        leder_annen_godtgjorelse = leder_annen_godtgjorelse * 1000
      ) |>
      # renaming for the purposes of the plot
      rename(
        Year = year,
        Salary = lederlonn,
        `Other compensation` = leder_annen_godtgjorelse
      ) |>
      # pivoting to join the two values to use fill
      pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |>
      ggplot(aes(Year, value, fill = Compensation)) +
      geom_col() +
      # using currency scale function to add correct currency code or ?
      currency_scale +
      # pretty colours
      scale_fill_met_d("Hokusai2", direction = -1) +
      labs(
        x = "", y = "", title = "CEO compensation"
      ) +
      theme(legend.position = "bottom") +
      theme_light()
  }

>>>>

```{r compensation_plot, out.width="100%", fig.cap="Based on the category \`Lederlønn' in the Proff.no data. Not in thousands. Includes the entries \`Lønn' and \`Leder annen godtgjørelse'. A common measure of transparency, but should normally be evaluated in context."}
## CEO compensation-----------------------------------------------------------
CEO_plot <-
  # Testing for the presence of data
  if (sum(!is.na(htmldata$lederlonn)) == 0 &&
    sum(!is.na(htmldata$leder_annen_godtgjorelse)) == 0) {
    # Returning NA if no data
    NA
  } else {
    # Creating plot if any data exist
    # Note that the plot will still look empty, but have a legend and scales,
    # if all values are explicit zeroes
    htmldata |>
      # preparing for pivoting
      select(
        year, lederlonn, leder_annen_godtgjorelse
      ) |>
      # Compensation in ordinary numbers
      mutate(
        lederlonn = lederlonn * 1000,
        leder_annen_godtgjorelse = leder_annen_godtgjorelse * 1000
      ) |>
      # renaming for the purposes of the plot
      rename(
        Year = year,
        Salary = lederlonn,
        `Other compensation` = leder_annen_godtgjorelse
      ) |>
      # pivoting to join the two values to use fill
      pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |>
      ggplot(aes(Year, value, fill = Compensation)) +
      geom_col() +
      # using currency scale function to add correct currency code or ?
      currency_scale +
      # pretty colours
      scale_fill_met_d("Hokusai2", direction = -1) +
      labs(
        x = "", y = "", title = "CEO compensation"
      ) +
      theme_light() +
      theme(legend.position = "bottom")
  }
